Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-18 chapters/discussion/discussion.tex
minor change

In \chapref{crosstransf}, we exploit overhead imagery to construct
the constraint function for the camera orientation and location.
We trained a CNN that can estimate the semantic layout of the ground
view image from the overhead image. During training, we learn the
pixel-to-pixel correspondences from the aerial image to the ground. We
project the semantic layout the of the overhead image to the ground
view with the learned correspondence.
When computing the output of the constraint function, we feed the
aerial image of the gien location and orientation to the network. By
comparing the aerial-to-ground with the real layout of the ground
image, we measure the consistency between the two and use
it as the value of our constraint function.
We also demonstrate the efficiency of our method for CNN pre-training
for aerial image segmentation.

>>>>

In \chapref{crosstransf}, we exploited overhead imagery to construct
the constraint function for the camera orientation and location.
We trained a CNN that can estimate the semantic layout of the ground
view image from the overhead image. During training, the CNN learns the
pixel-to-pixel correspondences from the aerial image to the ground
image. 
It then projects the semantic layout the of the overhead image to the
ground view according to the learned correspondence.
When computing the output of the constraint function, we feed the
aerial image of given location and orientation to the network. By
comparing the aerial-to-ground layout with the layout computed from
the ground image, we measure the consistency between these two and use
consistency value as the output of the constraint function. 
In our experiments, we also demonstrated the efficiency of our method
for pre-training CNNs for aerial image segmentation.
